Survey Results from: Meta-analytic approaches and new effect sizes to account for heterogeneous effects in comparative physiology

### 2021-07-14 R/survey_data_results.Rmd
Updated ccache

pacman::p_load(dplyr,ggplot2,here, pander, janitor)

@@

```{r}
dat %>% dplyr::group_by(stat_model_type) %>% janitor::tabyl(stat_model_type) %>%
  dplyr::summarise(MLMA = dplyr::if_else(grepl("multilevel meta-analysis", stat_model_type), n, 0),
                  MLMR = dplyr::if_else(grepl("meta-regression models", stat_model_type), n, 0),
                    LinearRegrs = dplyr::if_else(grepl("linear regression", stat_model_type), n, 0),
                 Other = dplyr::if_else(grepl("unclear/other", stat_model_type), n, 0),
                 Vote = dplyr::if_else(grepl("vote counting", stat_model_type), n, 0),
                 WeightedReg = dplyr::if_else(grepl("weighted regression including mixed effects models", stat_model_type), n, 0),
                 RE = dplyr::if_else(grepl("random-effects meta-analysis", stat_model_type), n, 0)) %>% 
  colSums(.) %>% data.frame(effect = names(.), n = .) %>% mutate(prop = (n / sum(n)*100)) %>% arrange(effect) %>% 
  ggplot() + tm + theme(axis.title.y = element_blank(),
                        axis.text.y = element_text(size=8)) +
  geom_col(aes(x = effect, y = n), width = 0.5, fill = background.colour, colour = text.colour, size = 0.5) +
  scale_y_continuous(expand=c(0,0),breaks=seq(1,20,2)) +
  labs(x = "Effect Size",
       y = "Number of Papers") +
  coord_flip()
```

>>>>

pacman::p_load(dplyr,ggplot2,here, pander, janitor, magrittr)

@@

```{r}
summary <-  dat %>% dplyr::group_by(stat_model_type) %>% janitor::tabyl(stat_model_type) %>%
  dplyr::summarise(`Multilevel Meta-analysis Model` = dplyr::if_else(grepl("multilevel meta-analysis", stat_model_type), n, 0),
                  `Multilevel Metaregression Model` = dplyr::if_else(grepl("meta-regression models", stat_model_type), n, 0),
                    `Linear Regression` = dplyr::if_else(grepl("linear regression", stat_model_type), n, 0),
                 Other = dplyr::if_else(grepl("unclear/other", stat_model_type), n, 0),
                 `Vote Counting` = dplyr::if_else(grepl("vote counting", stat_model_type), n, 0),
                 `Weighted Regression` = dplyr::if_else(grepl("weighted regression including mixed effects models", stat_model_type), n, 0),
                 `Random Effects Model` = dplyr::if_else(grepl("random-effects meta-analysis", stat_model_type), n, 0)) %>% 
  colSums(.) %>% data.frame(effect = names(.), n = .) %>% mutate(prop = (n / sum(n))) %>% arrange(effect)
rownames(summary) <- NULL

summary %>% 
  ggplot() + tm +
  geom_col(aes(x = effect, y = prop), width = 0.5, fill = "black", colour = text.colour, size = 0.5) +
  scale_y_continuous(expand=c(0,0),limits = c(0,0.4)) +
  labs(x = "Analytical Approach",
       y = "Frequency") +
  coord_flip()
```
